\section{Theoretical investigation}
In this section we analyse the impact on the analytic and numerical solution of an SDE given by a perturbation on the transport field. The theoretical investigation we present is needed in order to give a meaning to the results we find in the Darcy case. Since the velocity field is approximated by means of the Finite Elements method, we hope that the solution of an SDE that has the numerical approximation of the velocity field as transport term would converge to the solution of the SDE that uses the exact velocity field. Moreover, it can be costly to evaluate the Finite Element solution at each timestep of DEM or CEM, but an interpolation procedure can be exploited in order to obtain faster simulations. Hence, another source of perturbation is introduced, and a theoretical background is fundamental to strengthen the basis of our method.

\subsection{Analysis of perturbed SDEs}
Let us consider $(\Omega, \mathcal{A}, P)$ a complete probability space, $(W_1(t), t\geq 0), (W_2(t), t\geq 0)$ two $d$-dimensional standard Wiener processes not necessarily independent and a filtration $(\mathcal{F}(t), t \geq 0)$ such that $W_1(t), W_2(t)$ are $\mathcal{F}(t)$-measurable. Moreover, let us consider $\sigma \in \R,$ and a function $f\colon \R^d \rightarrow \R^d$ and the following SDE
\begin{equation}\label{eq:AppSDE}
\left \{
\begin{aligned}
	dX(t) &= f(X(t))dt + \sigma IdW_1(t), && 0 < t \leq T, \\
	X(0) &= X_0,
\end{aligned} \right .
\end{equation}
where $I$ is the identity matrix in $\R^{d\times d}$. Let us consider a perturbation of the transport field $f^\epl\colon \R^d \rightarrow \R^d$. Then, we consider the perturbed SDE 
\begin{equation}\label{eq:AppSDEPer}
\left \{
\begin{aligned}
	dX^\epl(t) &= f^\epl(X^\epl(t))dt + \sigma I dW_2(t), && 0 < t \leq T, \\
	X^\epl(0) &= X_0.
\end{aligned} \right .
\end{equation}
Finally, let us introduce the following notation. Given a function $F\colon \R^d \to \R$
\begin{equation*}
	\|F\|_{\infty} = \sup_{x\in \R^d} |F(x)|.
\end{equation*}
We can state the following preliminary result
\begin{lemma}\label{lem:Lemma1} With the notation above, let us consider $d = 1$, $W_1 = W_2 = W$ almost everywhere. If the following assumptions are verified for a constant $K > 0$
\begin{enumerate}
	\item $|f(x) - f(y)| \leq K|x - y|, \: \forall x,y \in \R$,
	\item $|f(x)| \leq K(1 + |x|), \: \forall x \in \R$,
\end{enumerate}
and if the solution $X^\epl(t)$ of \eqref{eq:AppSDEPer} exists, then $X^\epl(t)$ and $X(t)$ the solution of \eqref{eq:AppSDE} satisfy
\begin{equation*}
	\E \sup_{0 \leq t \leq T} |X^\epl(t) - X(t)|^2 \leq  2T^2 \|f - f^\epl\|_{\infty}^2 e^{2K^2T^2}.
\end{equation*}
\end{lemma}

\begin{proof}
For almost all $\omega \in \Omega$ 
\begin{equation*}
\begin{aligned}
	|X^\epl(t) - X(t)|^2  &= \Big|\int_0^t (f^\epl (X^\epl(s)) - f(X(s)))ds \Big|^2 \\
	&\leq T \int_0^t |f^\epl (X^\epl(s)) - f(X(s))|^2 ds  \\
	&\leq 2T \int_0^t |f^\epl (X^\epl(s)) - f(X^\epl(s))|^2 ds + 2T \int_0^t |f (X^\epl(s)) - f(X(s))|^2 ds \\
	&\leq 2T^2 \|f - f^\epl\|_{\infty}^2 + 2T^2K^2 \int_0^t |X^\epl(s) - X(s)|^2ds,
\end{aligned} 
\end{equation*}
where we applied Cauchy-Schwarz inequality, Young inequality, assumption 1 and the definition of $\|\cdot \|$ respectively. We then apply Gronwall's inequality, which gives 
\begin{equation}\label{eq:TheoryEpsilon}
	|X^\epl(t) - X(t)|^2 \leq  2T^2 \|f - f^\epl\|_{\infty}^2 e^{2K^2T^2}, \quad a.e.
\end{equation}
Since the right hand side of the inequality is independent of time and $\omega$, we can then take the supremum over time and the expectation at both sides, \textit{i.e.},
\begin{equation*}
	\E \sup_{0 \leq t \leq T} |X^\epl(t) - X(t)|^2 \leq  2T^2 \|f - f^\epl\|_{\infty}^2 e^{2K^2T^2},
\end{equation*}
which concludes the proof.
\end{proof}
\noindent We now consider the case of two independent Wiener processes.

\begin{lemma}\label{lem:Lemma2} With the notation above and the assumptions of Lemma \ref{lem:Lemma1}, let us consider $W_1$ independent of $W_2$ and $d = 1$. Then
\begin{equation*}	
	\E \sup_{0 \leq t \leq T} |X^\epl(t) - X(t)|^2 \leq 4T(T \|f - f^\epl\|_{\infty}^2 + 4\sigma^2) e^{2K^2T^2}.
\end{equation*}
\end{lemma}

\begin{proof} Let us compute the difference between $X^\epl(t)$ and $X(t)$. Applying Young's inequality, we get
\begin{equation*}
\begin{aligned}
	\E \sup_{0 \leq t \leq T} |X^\epl(t) - X(t)|^2 &\leq 2\E \sup_{0 \leq t \leq T}\Big|\int_0^t (f^\epl (X^\epl(s)) - f(X(s)))ds \Big|^2 \\
		&\quad + 2\sigma^2 \E \sup_{0 \leq t \leq T} \Big|\int_0^t dW_1(s) - \int_0^t dW_2(s)  \Big|^2.
\end{aligned}
\end{equation*}
Let us define $Z(t) := W_1(t) - W_2(t)$. The process $Z(t)$ is a Wiener process with variance $2t$, thus it is a martingale. Hence, we can apply Doob's maximal quadratic inequality (\textit{e.g.}, \cite[Page 11]{Protter2004}) to the second term, obtaining
\begin{equation*}
	\E \sup_{0 \leq t \leq T} \Big|\int_0^t dW_1(s) - \int_0^t dW_2(s)  \Big|^2 = \E \sup_{0 \leq t \leq T} | Z(t) |^2 \leq 4 \E |Z(T)|^2 = 8T.
\end{equation*}
For the first term, we can apply the same technique as in Lemma \ref{lem:Lemma1}. Therefore, we get the result
\begin{equation*}
	\E \sup_{0 \leq t \leq T} |X^\epl(t) - X(t)|^2 \leq (4T^2 \|f - f^\epl\|_{\infty}^2 + 16T\sigma^2) e^{2K^2T^2}.
\end{equation*}
\end{proof}
\noindent With those preliminary results, we can now consider the general case of a $d$-dimensional SDE.
\begin{theorem}\label{th:Prop} With the notation above and if there exists a real constant $K$ such that
\begin{enumerate}
	\item $\|f(x) - f(y)\| \leq K\|x - y\|, \: \forall x,y \in \R^d$,
	\item $\|f(x)\| \leq K(1 + \|x\|), \: \forall x \in \R^d$,
\end{enumerate}
then it is true for $X(t), X^\epl(t)$ the solutions of \eqref{eq:AppSDE} and \eqref{eq:AppSDEPer} that 
\begin{equation}\label{eq:Proposition}
	\E \sup_{0\leq t\leq T} \| X^\epl(t) - X(t) \|_2^2 \leq 4T\Big(T \sum_{i=1}^d \|f_i(x) - f_i^\epl(x)\|_\infty^2 + 4d\sigma^2\Big)e^{2dK^2T^2}.
\end{equation}
\end{theorem}
\begin{proof} The proof follows from Lemma \ref{lem:Lemma2}. Let us denote by $X_i(t), X_i^\epl(t)$ the $i$-th component of the solution, $i = 1, \dots, d$. Then
\begin{equation*}
\begin{aligned}
	\E\sup_{0\leq t\leq T} \|X^\epl(t) - X(t)\|^2  &= \E \sup_{0\leq t\leq T} \sum_{i=1}^d |X_i^\epl(t) - X_i(t)|^2 \\
		&\leq  \sum_{i=1}^d \E \sup_{0\leq t\leq T} |X_i^\epl(t) - X_i(t)|^2 \\
\end{aligned}
\end{equation*}
Then, applying Lemma \ref{lem:Lemma2} to each component of the solution, one obtains \eqref{eq:Proposition}.
\end{proof}

\begin{remark} \normalfont{\textbf{(convergence considerations.)} The result of Proposition \ref{th:Prop} shows that in case one uses two different Wiener processes $W_1, W_2$ for \eqref{eq:AppSDE} and \eqref{eq:AppSDEPer}, the strong convergence is not granted. In fact, while the first term in estimation \eqref{eq:Proposition} tends to zero due to the uniform convergence of the perturbed transport field towards the non-perturbed one, the error due to the different Wiener processes is independent of $\epl$. However, in underground flow models the variance $\sigma$ of the Brownian diffusion is often small with respect to the transport field. Therefore, one could consider the solution $X^\epl(t)$ of \eqref{eq:AppSDEPer} to be practically converging to the solution $X(t)$ of \eqref{eq:AppSDE} in case $f^\epl$ converges to $f$ with respect to $\epl$.}
\end{remark}

\begin{remark} \label{rem:Remark2} \normalfont{\textbf{(interpolation results.)} Let us consider an interval $D = [l, r] \subset \R$ where $f$ and $f^\epl$ are defined and $f^\epl$ to be a polynomial interpolation of $f$ on a grid $x_i = l + \epl i, i = 0, \dots, N, r = l + N\epl$. Then, the interpolation error of can be estimated if $f$ is regular enough. In particular, we can state the following results  
\begin{enumerate}
	\item If $f$ is Lipschitz continuous of constant $K$, and $f^\epl$ is its piecewise constant interpolation computed at the midpoint of each subinterval of the grid
		\begin{equation*}
			\sup_{x_i \leq x \leq x_{i+1}} |f(x) - f^\epl(x)| \leq K|x - \frac{x_i+x_{i+1}}{2}| \leq \frac{1}{2} K \epl, \: i = 0, \dots, N - 1.
		\end{equation*}
		Since $f$ is continuous
		\begin{equation*}
			\|f - f^\epl \|_{\infty} \leq \frac{1}{2} K \epl.
		\end{equation*}
	\item If $f$ is of class $\mathcal{C}^1$, $f^\epl$ is its piecewise constant interpolation and for a real constant $C_1$ \cite[Chapter 8]{Quarteroni2007}
		\begin{equation*}
			\|f - f^\epl\|_{\infty} \leq C_1 \epl \|f'(x)\|_{\infty}.
		\end{equation*}
	\item If $f$ is of class $\mathcal{C}^2$, $f^\epl$ is its piecewise linear interpolation and for a real constant $C_2$ \cite[Chapter 8]{Quarteroni2007}
		\begin{equation*}
			\|f - f^\epl\|_{\infty} \leq C_2 \epl^2 \|f''(x)\|_{\infty}.
		\end{equation*}
\end{enumerate}
In all these cases, $f^\epl$ converges uniformly to $f$ with respect to $\epl$, therefore the solution of \eqref{eq:AppSDEPer} converges to the solution of \eqref{eq:AppSDE} with respect to $\epl$. }
\end{remark}

\input{Darcy/DarcyTheoryNumerical}
\input{Darcy/DarcyTheoryExperiment}


