\section{Conclusion}

We investigated the stochastic particle tranport problem in the framework of underground flow. In particular, we analysed three numerical schemes that allow estimating the exit time of the solution of a general SDE from a bounded domain. Numerical experiments show that CEM seem to be the most appropriate choice in order to fulfill this purpose. In fact, estimating the probability of exit at each timestep using the Brownian bridge approach implies a small computational cost and improves dramatically the convergence of the classical Euler-Maruyama integration. On the other side, an adaptivity procedure we analysed based on the position of the iterate in the domain succeedes in restoring the weak order of the Euler-Maruyama scheme in an unbounded domain but does not imply a considerable advantage in computational time. Then, we managed to prove the properties of convergence of the analytical and numerical solution of a perturbed SDE to its non-perturbed solution. This is fundamental when an interpolation of the transport field is needed to increase computational speed. The convergence is confirmed by numerical results on a test case, where we succeeded in tuning the parameters of interpolation and time integration in order to having good performances. Finally, we applied the numerical schemes to the Darcy case, providing the details of a double Montecarlo simulation that can be exploited to estimate the exit time of a pollutant particle in the frame of the underground flow problem. Future improvements of the procedure explained in this work could be done employing Multi Level Montecarlo techniques for estimating the exit time in the Darcy case. Moreover, the modeling of extraction wells has not been taken into account, since we feel that the integration of the SDE in presence of singularities in the velocity field would have involved a deeper theoretical investigation and different numerical techniques.  
